\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Stanley Zheng}}\\
	New York, NY $\cdot$ stanley@zheng.nyc $\cdot$ 3473993732 $\cdot$ https://stanzheng.com\\
\end{center}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{City Of New York} \hfill New York, NY\\
\textit{Software Engineer} \hfill January 2018 - October\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Manaage and operate data pipelines on Google Cloud Platform.
\end{itemize}

\textbf{Cloudreach} \hfill New York, NY\\
\textit{Software Engineer} \hfill January 2018 - October 2019 \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked as a customer facing software engineer developing software on the cloud from strategy to delivery.
	\item Developed and maintained cloud-native data infrastructure on Google Cloud for a large government enterprise. – Used Google Cloud Services to ingest and transform data at the rate of 130K events per second to multi-tier consumers and datasinks; Data latency was \textless{} 5 seconds for events and managed over 48 TBs of data. – Designed and implemented CI/CD pipelines following Infrastructure-as-Code using Terraform and Jenkins.
	\item Designed and built data pipelines on AWS for large multimedia advertising companies on small teams. – Designed and deployed data lakes using AWS S3, Lambda, and Glue Crawlers transforming data to flat files. – Enabled data to perform data analytics on their data lakes and warehouses using Athena and Redshift.
\end{itemize}
\textbf{Dominion Enterprises - Homes.com} \hfill Norfolk, VA\\
\textit{Software Developer} \hfill March 2017 - November 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Spearheaded the platform rewrite of the Homes.com core product on a medium-sized team. – Designed architecture for microservices leveraging containerization and service orchestration on kubernetes. – Established code standard practices and style guidelines for the backend team through tooling and docs.
\end{itemize}
\textbf{Grow} \hfill Norfolk VA\\
\textit{Backend Software Developer} \hfill January 2015 - October 2016\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item ContentAds (2016). Lead developer on real-time dynamic ads system for Google and Rogers Canada. Developed an asset pipeline that transformed live video on-demand into assets trafficked to DoubleClick.
	\item Grow Gifts (2015). Full-stack developer on an ecommerce project. Developed custom internal CRM using React to handle orders and developed the Java backend that serviced the client and internal facing sites.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{Recurse Centter}\hfill New York NY\\
Paticipant Participated in a 12-week coding retreat at the Recurse Center in New York City. Improved programming skills through project based learning, mentoring, and pairing with other programmers. \hfill November 2016 - Feb 2017\\
\vspace{2mm}
\textbf{Old Dominion University}\hfill Norfolk, VA\\
Bachelors of Science Computer Science \hfill September 2010 - June 2015\\
\vspace{2mm}

\header{Volunteer Experience}
{\textbf{Brigade captain}}\\
CodeforAmerica Brigade Captain\\
\vspace*{2mm}

\header{Skills}
\begin{tabular}{ l l }
	Proficient Languages:         & JavaScript, HCL, Markdown, Python, SQL, YAML                                              \\
	Proficient Technologies:      & AWS, Docker, Git, GCP, Jenkins, Jupyter, Kubernetes, MySQL, Node, React, Redis, Terraform \\
	Some Experience Languages:    & C++, C\#, Cloud Init, CSS, Golang, HTML, Java, Lua, PHP                                   \\
	Some Experience Technologies: & Angular.js, Android, Atlassian Bamboo, Apache Airflow, Apache Beam                        \\
	-:                            & Angular.js                                                                                \\
\end{tabular}
\vspace{2mm}



\ 
\end{document}
